Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-06-21 assets/distribution_weights.tex
:bento: Update assets

\begin{axis}[%
width=4.036in,
height=3.396in,
at={(0.677in,0.458in)},
scale only axis,
xmin=1,
xmax=4,
xtick={1, 2, 3, 4},
xlabel style={font=\color{white!15!black}},
xlabel={Reflection State},
ymin=0,
ymax=1,
ylabel style={font=\color{white!15!black}},
ylabel={Probability Distribution},
axis background/.style={fill=white},
xminorgrids,
yminorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	0.249999734945382\\
2	0.250000264528953\\
3	0.25000026543652\\
4	0.249999735089145\\
};
\addlegendentry{$\rho =0$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	0.29621586579285\\
2	0.376168737406121\\
3	0.155469818621155\\
4	0.172145578179874\\
};
\addlegendentry{$\rho =0.02$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	0.262448276431783\\
2	0.712350409003269\\
3	0.00824022832841558\\
4	0.0169610862365327\\
};
\addlegendentry{$\rho =0.05$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	0.140066723576523\\
2	0.859156695957714\\
3	0.000133936954753823\\
4	0.000642643511009231\\
};
\addlegendentry{$\rho =0.1$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	0.00129716398391274\\
2	0.998702836015253\\
3	1.07370451326091e-15\\
4	8.33074594560992e-13\\
};
\addlegendentry{$\rho =1$}

>>>>

\begin{axis}[%
width=4.036in,
height=3.396in,
at={(0.677in,0.458in)},
scale only axis,
xmin=1,
xmax=4,
xtick={1, 2, 3, 4},
xlabel style={font=\color{white!15!black}},
xlabel={Reflection State},
ymin=0,
ymax=1,
ylabel style={font=\color{white!15!black}},
ylabel={Probability Distribution},
axis background/.style={fill=white},
xminorgrids,
yminorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot [color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}]
  table[row sep=crcr]{%
1	2.62331519807269e-06\\
2	0.999997376684802\\
3	4.89949641833056e-30\\
4	2.6174774451771e-24\\
};
\addlegendentry{$\rho =1$}

\addplot [color=mycolor2, dashed, line width=2.0pt, mark=+, mark options={solid, mycolor2}]
  table[row sep=crcr]{%
1	9.21083675347438e-06\\
2	0.812542727242104\\
3	0.187445044005617\\
4	3.01791552545155e-06\\
};
\addlegendentry{$\rho =0.15$}

\addplot [color=mycolor3, dotted, line width=2.0pt, mark=square, mark options={solid, mycolor3}]
  table[row sep=crcr]{%
1	1.56711271328569e-05\\
2	0.695664383940126\\
3	0.304312342609931\\
4	7.60232280996882e-06\\
};
\addlegendentry{$\rho =0.1$}

\addplot [color=mycolor4, dashdotted, line width=2.0pt, mark=x, mark options={solid, mycolor4}]
  table[row sep=crcr]{%
1	1.79207354228568e-05\\
2	0.591606048367841\\
3	0.408364572353122\\
4	1.14585436146039e-05\\
};
\addlegendentry{$\rho =0.05$}

\addplot [color=mycolor5, line width=2.0pt, mark=triangle, mark options={solid, mycolor5}]
  table[row sep=crcr]{%
1	2.61368383798461e-05\\
2	0.497964372118738\\
3	0.501988384568931\\
4	2.11064739508265e-05\\
};
\addlegendentry{$\rho =0$}
